---
title: "R Notebook"
output: html_notebook
---

A 2016 study from the CDC reported that more than a third of American aduts are not getting enough sleep on a regular basis. The national sleep foundation recommends that adults need between 7 to 9 hours of sleep per night to function well. Consistent sleep deprivation is known to increase risk of health problems, negatively affect cognitive processes, and contribute to depressive symptoms. 

The dataset nhanes.samp.adult contains sleep information for 135 participants ages 21 years of older. The variable SleepHrsNight contains the self-reported number of hours a participant usually gets at night on weekdays or workdays.


Load the data
```{r}
library(oibiostat)
data("nhanes.samp.adult")
```

1) Using numerical and graphical summaries, describe the distribution of nightly sleep in the dataset.

In addition, use a Shapiro test to formally test for normality.  For this test, a significant result indicates significant skew. 

```{r}
shapiro.test(???)
```

2) Conduct a hypothesis test to assess whether on average, American adults are getting enough sleep. Let mu be 8 hours. 

(a) Formulate null and alternative hypotheses

(b)Specify a significance level, alpha

(c)Calculate the test statistic

(d)Calculate the p-value. Although there is a large number of samples, use the t-distribution to calculate the the p-value to account for the fact that the population sd is unknown.

Instead of calculating the test statistic and p-value as you did above you can also use the function t.test() to calculate the p-value:

Complete the function below by inputting the data, mu, and what the alternative hypothesis is (you can entere here "two.sided", "less", or "greater"). Do the results below match that of what you found?
```{r}
t.test(data, mu = ?, alternative = ?)
```

Interpret the p-value in the context of the decided alpha. 

Notice above what t.test returns. How can you use t.test to find the 95% confidence interval?
